Final Project Code ALL

### 2022-12-09 Draft_Final_Code.Rmd
Complete Draft of Final Code

### Model Spec, Recipes, and Workflows for Linear Regression Model

@@

## Perform LASSO for Subset Selection

@@

lasso_wf_tune <- workflow() %>% 
  add_recipe(data_rec_lasso) %>%
  add_model(lm_lasso_spec_tune)

@@

@@

### Evaluation Metrics

@@

### Evaluation Metrics

@@

### Visualize Residuals for Final GAM

@@

## Compare All Linear Regression Model Performance

@@

### Adds Variable for Odds Ratio

@@

@@

# Cross Validation and Evaluation Metrics

@@

### Obtain Evaluation Metrics

@@

```{r}
imdb_clean %>%
  count(Genre_1)

imdb_clean %>%
  count(Genre_2)

imdb_clean %>%
  count(New_Genre)
```

@@

imdb_clean %>%
  group_by(kclust_8) %>%
  count(Genre_1)

imdb_clean %>%
  group_by(kclust_8) %>%
  count(Genre_2)

imdb_clean%>%
  count(kclust_8)
```

```{r}
imdb_clean %>%
  ggplot(aes(x = kclust_8, fill = Genre_1)) +
    geom_bar(position = "fill") +
    labs(x = "Cluster") + 
    theme_classic()

imdb_clean %>%
  ggplot(aes(x = kclust_8, fill = Genre_2)) +
    geom_bar(position = "fill") +
    labs(x = "Cluster") + 
    theme_classic()

imdb_clean %>%
  ggplot(aes(x = kclust_8, fill = New_Genre)) +
    geom_bar(position = "fill") +
    labs(x = "Cluster") + 
    theme_classic()

@@

### Hierarchial Clustering

```{r}
# Random subsample of 50 penguins
set.seed(253)
imdb_hc <- imdb_clean %>%
    slice_sample(n = 25)

@@

# Compute a distance matrix on the scaled data
dist_mat_scaled <- dist(scale(imdb_hc_sub))

dist_mat_full <- dist(scale(imdb_hc_full))
```

```{r}
imdb_hc_avg <- hclust(dist_mat_scaled, method = "average")
imdb_full_avg <- hclust(dist_mat_full, method = "average")

# Plot dendrogram
plot(imdb_hc_avg)
```

@@

plot(imdb_hc_avg, labels = paste(imdb_hc$Genre_1, imdb_hc$Genre_2))
```

```{r}
imdb_clean <- imdb_clean %>%
    mutate(
        hclust_num = factor(cutree(imdb_full_avg, k = 3)) # Cut into 6 clusters (k)
    )

```{r}
ggplot(imdb_clean, aes(x = hclust_num, fill = Genre_1)) +
    geom_bar(position = "fill") +
    labs(x = "Cluster") + 
    theme_classic()
```

>>>>

### Model Spec, Recipes, and Workflows

@@

## Perform LASSO for Subset Selection (Regression Model)

### Model Spec, Recipes, and Workflow

@@

lasso_wf_tune <- workflow() %>% 
  add_recipe(data_rec_lasso) %>%
  add_model(lm_lasso_spec_tune) 
```

### Tune Model and Cross Validation

@@

### Obtain Evaluation Metrics for Lasso Model

@@

### Obtain Evaluation Metrics for GAM1

@@

### Obtain Evaluation Metrics for GAM2

@@

### Visualize Residuals for Final GAM (GAM1)

@@

## Compare All Regression Model Performance

@@

### Add Variable for Odds Ratio

@@

### Cross Validation and Evaluation Metrics

@@

@@

### Obtain Evaluation Metrics for Logistic Regression

@@

# Count of Movies per Genre (Primary Genre)
imdb_clean %>%
  count(Genre_1)

# Count of Movies per Genre (Secondary Genre)
imdb_clean %>%
  count(Genre_2)

# Count of Movies per Genre (Overall Genre)
imdb_clean %>%
  count(New_Genre)
```

@@

# How many of each Genre 1 in each cluster
imdb_clean %>%
  group_by(kclust_8) %>%
  count(Genre_1)

# How many of each Genre 2 in each cluster
imdb_clean %>%
  group_by(kclust_8) %>%
  count(Genre_2)

# How many movies in each cluster
imdb_clean%>%
  count(kclust_8)
```

#### Visualizations of Genres in Each Cluster

# Genre 1
imdb_clean %>%
  ggplot(aes(x = kclust_8, fill = Genre_1)) +
    geom_bar(position = "fill") +
    labs(x = "Cluster") + 
    theme_classic()

# Genre 2
imdb_clean %>%
  ggplot(aes(x = kclust_8, fill = Genre_2)) +
    geom_bar(position = "fill") +
    labs(x = "Cluster") + 
    theme_classic()

# Overall Genre
imdb_clean %>%
  ggplot(aes(x = kclust_8, fill = New_Genre)) +
    geom_bar(position = "fill") +
    labs(x = "Cluster") + 
    theme_classic()

@@

## Hierarchial Clustering

### Set up Clustering and Distance Matrix

```{r}
# Random subsample of 25 Movies
set.seed(253)

imdb_hc <- imdb_clean %>%
    slice_sample(n = 25)

@@

# Compute a distance matrix on the scaled data
dist_mat_scaled <- dist(scale(imdb_hc_sub))     # Subset Distance Matrix

dist_mat_full <- dist(scale(imdb_hc_full))      # Full Data Distance Matrix
```

```{r}
imdb_hc_avg <- hclust(dist_mat_scaled, method = "average")    # Subset
imdb_full_avg <- hclust(dist_mat_full, method = "average")    # Full Data

### Visualize Dendrograms

```{r}
# Plot dendrogram on Subset
plot(imdb_hc_avg)
```

```{r}
# Adding Genre Labels

@@

plot(imdb_hc_avg, labels = paste(imdb_hc$Genre_1, imdb_hc$Genre_2))

plot(imdb_hc_avg, labels = paste(imdb_hc$Genre_1, imdb_hc$Genre_2, imdb_hc$Genre_3))

plot(imdb_hc_avg, labels = paste(imdb_hc$New_Genre))
```

### Cutting the Tree

```{r}
imdb_clean <- imdb_clean %>%
    mutate(
        hclust_num = factor(cutree(imdb_full_avg, k = 3)) # Cut into 6 clusters (k)
    )
```

### Visualizing Genres in Final Clusters (Full Data)

```{r}
ggplot(imdb_clean, aes(x = hclust_num, fill = Genre_1)) +
    geom_bar(position = "fill") +
    labs(x = "Cluster") + 
    theme_classic()

ggplot(imdb_clean, aes(x = hclust_num, fill = New_Genre)) +
    geom_bar(position = "fill") +
    labs(x = "Cluster") + 
    theme_classic()

ggplot(imdb_clean, aes(x = Budget, y = Gross, color = hclust_num)) +
    geom_point() +
    theme_classic()
```
